% This document is compiled using pdfLaTeX
\documentclass[11pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{parskip}
\usepackage{amsfonts}
\usepackage{graphicx}
\setlist[itemize]{left=0pt, itemsep=2pt, topsep=4pt}
\setlength{\parskip}{4pt}

% Simple commands
\newcommand{\ContactInfo}[3]{\small#1 \\
	\href{#2}{#2} \\ #3}

\begin{document}
\raggedright

% Header
\begin{center}
	{\LARGE\bfseries Md. Tanzid Haque}\\[6pt]
	{\normalsize Software Developer}\\[6pt]
	\vspace{2pt}
	\href{https://tanzid.dev}{tanzid.dev} $\vert$ \href{https://github.com/tanzid64}{github.com/tanzid64} $\vert$ \href{https://linkedin.com/in/tanzid64}{linkedin.com/in/tanzid64}\\
	Email: \href{mailto:tanzid3@gmail.com}{tanzid3@gmail.com} $\vert$ Phone: +880 17089-15045
\end{center}

\vspace{6pt}
\hrule
\vspace{10pt}

\vspace{6pt}

% Professional Summary
\section*{\scshape Professional Summary}
Full Stack Software Developer with over 2+ years of professional experience delivering SaaS, ERP, and e-commerce platforms using Laravel, React, and Next.js. Proven expertise in database and API optimization, secure payment integrations (Stripe, SSLCOMMERZ, Square), real-time systems, and VPS-based CI/CD deployment, with a strong focus on building scalable, production-ready applications.

% Technical Skills
\section*{\scshape Technical Skills}
\begin{tabularx}{\textwidth}{@{}l X@{}}
Languages: & PHP, JavaScript, TypeScript, Python \\
Frameworks: & Laravel, React, Next.js, TanStack, Django \\
Frontend: & Inertia.js, Tailwind CSS, Shadcn UI, Bootstrap \\
Databases: & MySQL, MongoDB, Redis \\
Tools: & Git, VPS, CI/CD (GitHub Actions), Postman \\
Libraries: & TanStack Query, TanStack Table, TanStack Form, React Hook Form \\
Familiar: & Docker, IoT
\end{tabularx}

% Experience
\section*{\scshape Experience}
\textbf{Laravel Developer} \hfill Sep 2025 -- Present\\
Kiwii IT, Dhaka
\begin{itemize}
	\item Built role-based permission and token-based authentication systems (Sanctum, JWT).
	\item Optimized database queries from 3s to under 500ms without caching.
	\item Integrated secure payment gateways (SSLCOMMERZ, Stripe).
	\item Implemented real-time notifications (Reverb, Pusher, SMS, Email).
	\item Deployed queue management using Laravel Horizon.
	\item Generated PDF invoices, reports, and Excel/CSV exports.
	\item Implemented presigned video uploads with Cloudflare R2.
	\item Managed VPS, CI/CD pipelines, and production deployments.
\end{itemize}
\vspace{8pt}

\textbf{Software Developer (Part-time)} \hfill Jul 2024 -- Present\\
Digiwinners, Dhaka
\begin{itemize}
	\item Developed secure APIs and admin panels for e-commerce platforms.
	\item Optimized applications using Redis caching.
	\item Payment System Integration: SSLCommerz, Stripe, Square.
	\item Handled VPS setup and automated deployment pipelines.
\end{itemize}
\vspace{8pt}

\textbf{Junior Software Developer} \hfill Jan 2025 -- Aug 2025\\
Consultech Solution BD
\begin{itemize}
	\item Developed ERP modules with permission-based access control.
	\item Built reusable UI components supporting large datasets (100k+ records).
	\item Designed dashboards for distributors and outlets.
	\item Implemented real-time updates and PDF reporting.
\end{itemize}
\vspace{10pt}

% Education
\section*{\scshape Education}
\textbf{B.Sc. in Electrical and Electronic Engineering} \\Green University of Bangladesh \hfill GPA: 3.49/4.00

% Languages
\section*{\scshape Languages}
Bangla (Native), English (Academic)

% Projects
\section*{\scshape Selected Projects}
\textbf{PingPanda — SaaS Website Monitoring Platform} \hfill Next.js, Prisma, TanStack Query\\
\begin{itemize}[left=0pt]
	\item Built a real-time website event tracking system to monitor uptime, API health, and user events.
	\item Implemented Clerk-based authentication with API key generation and secure request validation.
	\item Designed webhook endpoints to receive and process external service events.
	\item Integrated Discord bot for instant alert delivery on system failures and threshold breaches.
	\item Used Prisma ORM and TanStack Query to ensure scalable data fetching and caching.
\end{itemize}
\vspace{8pt}

\textbf{PDF Craft — AI-Powered PDF Chat SaaS} \hfill Next.js, OpenAI, Stripe\\
\begin{itemize}
	\item Built a SaaS platform allowing users to upload PDFs and query content using AI-powered semantic search.
	\item Implemented vector embeddings and similarity search for accurate document retrieval.
	\item Developed secure authentication and subscription billing using Stripe.
	\item Optimized large PDF rendering and text extraction using React-PDF and server-side processing.
	\item Implemented usage limits, payment verification, and protected API routes.
\end{itemize}
\vspace{8pt}

\textbf{Big Data Import / Export System} \hfill Django, Celery, Redis, PostgreSQL\\
\begin{itemize}
	\item Developed high-volume CSV import and export pipelines handling large datasets without blocking the main application.
	\item Implemented background processing using Celery and Redis for long-running jobs.
	\item Created custom Django management commands for automated data ingestion and cleanup.
	\item Built email delivery of exported reports with secure file handling and job status tracking.
\end{itemize}

\vfill
\begin{center}
	Last updated: \today
\end{center}

\end{document}
